What is disputed on the web?

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
Minor edits

We argue why such a corpus of dispupted claims is useful for a wide range of applications related to information credibility on the web, and we look at what our current corpus reveals about what is being disputed on the web.

@@

We identify disputed claims by searching for lexical patterns such as ``the misconception that $S$'' (Section~\ref{findingclaims}). For example, if a page contains the text ``the minconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim. In Figure~\ref{templates} we list some of the patterns we used. In practice, many of the strings that match such a pattern are not well-formed disputed claims. We use a statistical classifier to filter out those strings that appear to make a well-formed claim.

We believe that this corpus will be useful for many purposes. We are currently using it as part of our Dispute Finder~\cite{Ennals2010} project to automatically highlight phrases on web pages that are disputed by other sources. We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, and visualization tools that let users know what is disputed about a topic that interests them, and statistical tools that allow people to look for patterns in internet debate  (Section~\ref{using}).

We have made our corpus publicly available for other researchers to download at \url{http://confront.intel-research.net/}. In currently contains claims extracted from pages written on the days between October 1st 2009 and January 19th 2010, and pages written on January 10th of every year from 2000 to 2010. This amounts to approxmately 1.1 million strings that we believe are making disputed claims. We plan to expand our corpus as we crawl more of the web and improve our algorithms.

@@

There are several ways that a user can determine whether to trust information that they find on a web page. The user can check the reputation of the person or organization that wrote the web page; they can check whether the web page looks like a they think a reliable web page should look; or they can check whether the information is consistent with information available from other sources.

@@

In our research, we are following the third approach. We aim to inform users when information that they encounter is disputed by another source. We have built an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs users when a web page that they are reading makes a claim that it knows to be disputed. For example, if a user is reading a page that says ``Elvis is Alive'' then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view. In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to enter disputed claims manually, and scraping a small set of web sites that manually curate such claims (currently Politifact.org and Snopes.com); however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.

@@

There has been significant work on detecting contradictions. Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding. de Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradictions. AuContraire~\cite{Ritter} uses TextRunner~\cite{Etzioni2008,Banko2008} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction. Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another. The RTE-3 Recognizing Textual Entailment challenge~\cite{Giampiccolo2007} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.

Detecting contradictions has proven to be a hard problem~\cite{Giampiccolo2007}. Much of the difficulty comes from the fact that one typically needs deep semantic knowledge to determine whether two statements that look like they might contradict each other actually do. For example ``George Bush is married to Barbara Bush'' does not contradict ``George Bush is married to Laura Bush'' because there is more than one George Bush. ``Alan Turing was born in England'' does not contradict ``Alan Turing was born in London'' because London is in England. ``It is raining is San Francisco'' does not contradict ``It is not raining in San Francisco'' if the statements were made at different times.

@@

We implemented a three stage process to build our corpus of disputed claims, each described in the following Sections. We first create a set of lexical patterns such as ``the misconception that'' and ``it is not the case that'' (Section~\ref{patterns}). We then search the Web for these patterns (Section~\ref{searchpattern}). Finally, we filter the resulting strings to give only those that resemble unambiguous disputed claims (Section~\ref{filterclaim}).

@@

This is an instance of template inference (aka pattern matching), a method that has been used extensively for many NLP tasks. Hearst~\cite{Hearst1992} searched for templates such as ``$X$ such as $Y$'' to infer hyponyms, Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events. TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
These methods differ on how {\bf finish here}
\x{add more related work here}
\todo{add more related work here}

In this work we simply start with an initial set of patterns that we wrote by hand. We then found additional templates by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim. From this set of candidate prefix patterns, we manually selected additional patterns.

@@

Rather that searching for an arbitrary collection of known disputed claims, we found that we generated better templates by searching for claims that most documents disagee with (e.g. ``eskimos have many words for snow'') rather than claims that many people agree with (e.g. ``there is a God''). If many people agree with a claim is true then many of the patterns that we find will not be patterns that indicate that the claim is disputed.

@@

Since we are interested in the time information of the claims and we want to be able to incrementally update our corpus as new pages appear on the web, without repeatedly downloading the same pages, we need to be able to request only pages updated in a given date range. The Yahoo BOSS API does not offer the ability to do so; we thus simulate this behaviour by instead including a literal date string in our queries. For example, if we want to find claims that were disputed on January 4th 2010 then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.

The reasoning behind this technique is that many articles on the web include the date the article was posted in the text of the web page, particularly news articles and blog posts. This approach has false positives and false negatives. Some web pages include dates that are not the date the article was posted, and some web pages either don't include the date the article was posted, or write their date in a different format. Indeed our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first).

@@

Not every chunk of text identified by one of our patterns is a well-formed disputed claim. Consider for example the text chunks in Figure~\ref{filtered}. A chunk of text might not be a statement (case 1), it might include unbound referents such is ``it'', or ``they'' (case 2), or it might only make sense within the context of a particular document (case 3).

@@

Dispute analysis agents that run in the background represent another application we see for a corpus of disputed claims. Such agents could be trained with information regarding the books, journals, and news articles a user reads. It would then be able to alert the user when a previously-read source is now disputed. It could also track a set of topics and tell the user when something new is disputed about a topic. A background dispute analysis agent would serve as an automated research assistant, alerting me when

A third category of applications could be broadly classified as research tools: agents which allow users to explore what is disputed about a particular topic, or to more broadly examine the zeitgeist of disputes. In this way the cultural

Recognizing that these are but a few of the ways in which a disputed claim corpus could be used, we will release this data set to the research community as a whole.

\x{"It will be available for unrestricted use under the XXX license. The dataset can be accessed at http://xxx.intel.com/xxx"}

@@

Our research has shown that the web can be used as a corpus to determine what claims people identify as being disputed. Although it is likely that any specific claim found on the web is not authoritative, the web as a whole aggregates the array of views to be found online.

Furthermore, because individuals express opinions freely online, a snapshot of the disputed claims online can provide valuable insights into the cultural zeitgeist of the time.

>>>>

We argue why such a corpus of disputed claims is useful for a wide range of applications related to information credibility on the web, and we look at what our current corpus reveals about what is being disputed on the web.

@@

We identify disputed claims by searching for lexical patterns such as ``the misconception that $S$'' (Section~\ref{findingclaims}). For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim. In Figure~\ref{templates} we list some of the patterns we used. In practice, many of the strings that match such a pattern are not well-formed disputed claims. We use a statistical classifier to filter out those strings that appear to make a well-formed claim.

We believe that this corpus will be useful for many purposes. We are currently using it as part of our Dispute Finder~\cite{Ennals2010} project to automatically highlight phrases on web pages that are disputed by other sources. We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, visualization tools that let users know what is disputed about a topic that interests them, and statistical tools that allow people to look for patterns in internet debate  (Section~\ref{using}).

We have made our corpus publicly available for other researchers to download at \url{http://confront.intel-research.net/}. It currently contains claims extracted from pages written on the days between October 1st 2009 and January 19th 2010, and pages written on January 10th of every year from 2000 to 2010. This amounts to approxmately 1.1 million strings that we believe are making disputed claims. We plan to expand our corpus as we crawl more of the web and improve our algorithms.

@@

There are several ways that a user can determine whether to trust information that they find on a web page. The user can check the reputation of the person or organization that wrote the web page; they can observe whether the web page meets their aesthetic criteria for a reliable web page; or they can check whether the information is consistent with information available from other sources.

@@

In our research, we are following a third approach. We aim to inform users when information that they encounter is disputed by another source. We have built an extension to the Firefox web browser called Dispute Finder~\cite{Ennals2010} that informs users when a web page that they are reading makes a claim that it knows to be disputed. For example, if a user is reading a page that says ``Elvis is Alive'' then Dispute Finder will highlight that statement as being disputed and direct the user to other sources that put forward alternative points of view. In its currently released version, Dispute Finder builds a corpus of disputed claims by allowing users to enter disputed claims manually, and scraping a small set of web sites that manually curate such claims (currently Politifact.org and Snopes.com); however it is difficult to make this approach scale to the huge number of claims on the web that are disputed.

@@

There has been significant work on detecting contradictions. Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding. De Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradictions. AuContraire~\cite{Ritter} uses TextRunner~\cite{Etzioni2008,Banko2008} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction. Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another. The RTE-3 Recognizing Textual Entailment challenge~\cite{Giampiccolo2007} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.

Detecting contradictions has proven to be a hard problem~\cite{Giampiccolo2007}. Much of this difficulty comes from the fact that one typically needs deep semantic and contextual knowledge to determine whether two statements that look like they might contradict each other actually do. For example ``George Bush is married to Barbara Bush'' does not contradict ``George Bush is married to Laura Bush'' because there is more than one George Bush. ``Alan Turing was born in England'' does not contradict ``Alan Turing was born in London'' because London is in England. ``It is raining is San Francisco'' does not contradict ``It is not raining in San Francisco'' if the statements were made at different times.

@@

We implemented a three-stage process to build our corpus of disputed claims, each described in the following Sections. We first create a set of lexical patterns such as ``the misconception that'' and ``it is not the case that'' (Section~\ref{patterns}). We then search the Web for these patterns (Section~\ref{searchpattern}). Finally, we filter the resulting strings to give only those that resemble unambiguous disputed claims (Section~\ref{filterclaim}).

@@

This is an instance of template inference (aka pattern matching), a method that has been used extensively for many NLP tasks. Hearst~\cite{Hearst1992} searched for templates such as ``$X$ such as $Y$'' to infer hyponyms, and Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events. TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
These methods differ on how {\bf finish here}
\x{add more related work here}
\todo{add more related work here}

In this work we start with an initial set of manually crafted search patterns. We then identified additional templates by searching for the text of known disputed claims, and observing what text commonly occurred as a prefix of a known disputed claim. From this set of candidate prefix patterns, we manually selected additional patterns.

@@

Rather that searching for an arbitrary collection of known disputed claims, we found that we generated better templates by searching for claims that most documents disagee with (e.g. ``eskimos have many words for snow'') rather than claims that many people agree with (e.g. ``there is a God''). If many people agree that a claim is true then many of the patterns that we find will not be patterns that indicate that the claim is disputed.

@@

Since we are interested in the time information of the claims and we want to be able to incrementally update our corpus as new pages appear on the web without repeatedly downloading the same pages, we need to be able to request only pages updated in a given date range. The Yahoo BOSS API does not offer the ability to do so; we thus simulate this behaviour by instead including a literal date string in our queries. For example, if we want to find claims that were disputed on January 4th 2010 then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.

The reasoning behind this technique is that many articles on the web include the date the article was posted in the text of the web page, particularly news articles and blog posts. This approach has false positives and false negatives. Some web pages include dates that are not the date the article was posted, some web pages do not include the date the article was posted, and many web pages include dates in a different format. We recognize that our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first).

@@

Not every chunk of text identified by one of our patterns is a well-formed disputed claim. Consider for example the text chunks in Figure~\ref{filtered}. A chunk of text might not be a statement (case 1), it might include unbound referents such is ``it'' or ``they'' (case 2), or it might only make sense within the context of a particular document (case 3).

@@

Dispute analysis agents that run in the background represent another application we see for a corpus of disputed claims. Such agents could be trained with information regarding the books, journals, and news articles a user reads. It would then be able to track these subjects and alert the user when a previously-read source is now disputed. It could also track a set of topics and tell the user when something new is disputed about a topic. A background dispute analysis agent would thus serve as an automated research assistant.

A third category of applications could be broadly classified as research tools: agents which allow users to explore what is disputed about a particular topic, or to more broadly examine the zeitgeist of disputes. As an increasing proportion of human knowledge is brought to the web, these tools will be increasingly important in sociological and historical research.

@@

Our research has shown that the web can be used as a corpus to determine what claims people identify as being disputed. Although it is likely that any specific claim found on the web is not authoritative, the web as a whole aggregates the array of views to be found online. Furthermore, because individuals express opinions freely online, a snapshot of the disputed claims online can provide valuable insights into the cultural zeitgeist of the time.
